Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-03-19 draftfinalreport_v2.Rnw
added additional plots

>>>>

\begin{figure}
\begin{center}
<<fig=TRUE,echo=FALSE,width = 15,height=12>>=
ggplot(tp, aes(merge, cases, fill=Ethnicity)) + 
+     geom_bar(stat="identity", position="dodge")+
+     # theme(text=element_text(size=45))+
+     ylab("cases")+theme(axis.text.x = element_text(angle = 90, hjust = 0))
@
\end{center}
\caption{test}
%\label{fig:test}
\end{figure}

\begin{figure}
\begin{center}
<<fig=TRUE,echo=FALSE,width = 15,height=12>>=
tpsub$order <- factor(tpsub$merge, as.character(tpsub$merge))
ggplot(tpsub, aes(x=order, cases, fill=Ethnicity)) +
     geom_bar(stat="identity", position="dodge")+
     # theme(text=element_text(size=45))+
     ylab("cases")+theme(axis.text.x = element_text(angle = 90, vjust=0,hjust = 0))
@
\end{center}
\caption{test}
%\label{fig:test}
\end{figure}

\begin{figure}
\begin{center}
<<fig=TRUE,echo=FALSE,width = 15,height=12>>=
ggplot(tpsub, aes(x=order, perCap, fill=Ethnicity)) +
     geom_bar(stat="identity", position="dodge")+
     # theme(text=element_text(size=45))+
     ylab("per capita")+theme(axis.text.x = element_text(angle = 90, vjust=0, hjust = 1))
@
\end{center}
\caption{test}
%\label{fig:test}
\end{figure}

\begin{figure}
\begin{center}
<<fig=TRUE,echo=FALSE,width = 15,height=12>>=
tpsub1<-tpsub[ order(tpsub$Age), ]
tpsub1$order <- factor(tpsub1$merge, as.character(tpsub1$merge))
ggplot(tpsub1, aes(order, cases, fill=Ethnicity)) +
     geom_bar(stat="identity", position="dodge")+
     # theme(text=element_text(size=45))+
     ylab("cases")+theme(axis.text.x = element_text(angle = 90, hjust = 0))
@
\end{center}
\caption{test}
%\label{fig:test}
\end{figure}

\begin{figure}
\begin{center}
<<fig=TRUE,echo=FALSE,width = 15,height=12>>=
ggplot(tpsub1, aes(order, perCap, fill=Ethnicity)) +
     geom_bar(stat="identity", position="dodge")+
     # theme(text=element_text(size=45))+
     ylab("per captita")+theme(axis.text.x = element_text(angle = 90, hjust = 0))
@
\end{center}
\caption{test}
%\label{fig:test}
\end{figure}
